Bow shocks, bow waves, and dust waves

### 2018-05-23 papers/Papers1234/sec-dust-bow-intro.tex
Start writing up gas-grain decoupling

If the radiation field is sufficiently strong, then the collisional coupling between grains and gas will break down.

>>>>

If the radiation field is sufficiently strong, then the collisional
coupling between grains and gas will break down.  In this section, we
calculate the regions of star+stream parameter space where this might
occur, leading to a separation of the bow into an outer dust wave and
an inner, dust-free bow shock.

The drag force on a charged dust grain moving at a relative speed
\(w\) through a plasma has contributions from both direct collisions
and from electrostatic Coulomb interactions with ions and electrons.
We use the expressions in \citet{Draine:1979a}, equations~(4)--(6),
summing over protons, electrons, and helium ions.\footnote{Helium is
  assumed to be 50\% neutral and 50\% singly ionized, leading to only
  a small contribution to the drag force.  For much hotter stars, such
  as the central stars of planetary nebulae, helium may be doubly
  ionized, which leads to a more significant drag contribution,
  especially around \(w \approx \SI{5}{km.s^{-1}}\).} %
Results are shown in Figure~\ref{fig:gas-grain-drag-photoionized} for
different values of \(\phi = e U / kT\), where \(U = e Z\grain / a \) is
the electrostatic potential of a grain of charge \(Z\grain\) and
radius \(a\).
